\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-19 main.tex

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

Figure~\ref{fig:squid-layouts}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: $I1$, which separates BE and W1, and $I2$, which separates W1 and W2. Table~\ref{table:squid-layers}.

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|}
\hline
Layer name        & Thickness [nm] & Films located in layer \\ \hline
\hline
BE (bottom) & 160            & Field coil, pickup loop shield      \\ \hline
I1          & 150            & ---                                 \\ \hline
W1          & 100            & Pickup loop, field coil shield      \\ \hline
I2          & 130            & ---                                 \\ \hline
W2 (top)    & 200            & Pickup loop shield, modulation coil \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{kirtley_scanning_2016} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

>>>>

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.png}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: $I1$, which separates BE and W1, and $I2$, which separates W1 and W2. Table~\ref{table:squid-layers}.

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|}
\hline
Layer name        & Thickness [nm] & Films located in layer \\ \hline
\hline
BE (bottom) & 160            & Field coil, pickup loop shield      \\ \hline
I1          & 150            & ---                                 \\ \hline
W1          & 100            & Pickup loop, field coil shield      \\ \hline
I2          & 130            & ---                                 \\ \hline
W2 (top)    & 200            & Pickup loop shield, modulation coil \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M=\Phi_\mathrm{PL} / I_\mathrm{FC}$. Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large''). The wiring layers BE, W1, and W2 are shown in blue, orange, and green respectively. Middle row (b): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE). Bottom row (c): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$. For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}. The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles. The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.}
    \label{fig:squid-mutuals}
\end{figure*}
